Variants on the Flight and Maintenance Planning problem

### 2018-09-18 latex/notes/model/model.tex
changes to model and simulation document.

    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq C^{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
        % & \sum_{t \in \mathcal{T}, i \in \mathcal{I}} m_{it} \leq C^{max} \label{eq:capacity1}\\
        % availability
       % & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t + D_t\leq u_{max} 
       %  &t \in \mathcal{T} \label{eq:avalaibility1}\\
        % min assignments:
        & \sum_{i \in \mathcal{I}_j} a_{jti} = R_j
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        % just doing one thing at any given time:
        & \sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    \begin{align}
        % remaining used time
         & u_{it} \geq \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j 
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage}\\
         & u_{it} \geq u^{min} (1 - \sum_{t' \in \mathcal{T}^{s}_t} m_{it'})
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage}\\
         & u_{it} \in [0, \max_j{\{H_j\}}]
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage_lower}\\
         & rut_{it} \leq rut_{i(t-1)} + H^{M} m_{it} - u_{it}
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\
        & rut_{i0} = Rut^{Init}_i
               & i \in \mathcal{I} \label{eq:rut_initial}\\
        & rut_{it} \geq H^{M} m_{it'}
                & t \in \mathcal{T}, t' \in \mathcal{T}^{s}_t, i \in \mathcal{I}\label{eq:rut_lower}\\ 
        & rut_{it} \in [0,H^{M}]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu}              
        % & ret_{it} \leq ret_{it-1} - 1 + \sum_{t' \in \mathcal{T}^{st}_t} s_{it'} + E m_{it}
        %         & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:ret_upper}\\
        % & ret_{i0} = Ret^{Init}_i
        %         & i \in \mathcal{I} \label{eq:ret_initial}\\
        % & ret_{it} \geq E m_{it}
        %         & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:ret_lower}\\                 
        % & ret_{it} \in [0,E]
        %         & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:me}\\
        % & \sum_{i \in \mathcal{I}} ret_{it} \geq Ret^{Init}_{sum}
        %       & t = |\mathcal{T}| \label{eq:min_ret}\\
        % & \sum_{i \in \mathcal{I}} rut_{i|\mathcal{T}|} \geq Rut^{Init}_{sum}\\
    \end{align}

>>>>

    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq C^{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
        % & \sum_{t \in \mathcal{T}, i \in \mathcal{I}} m_{it} \leq C^{max} \label{eq:capacity1}\\
        % availability
       % & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t + D_t\leq u_{max} 
       %  &t \in \mathcal{T} \label{eq:avalaibility1}\\
        % min assignments:
        & \sum_{i \in \mathcal{I}_j} a_{jti} \geq R_j
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        % just doing one thing at any given time:
        & \sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    \begin{align}
        % remaining used time
         & u_{it} \geq \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j 
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage1}\\
         & u_{it} \geq u^{min} (1 - \sum_{t' \in \mathcal{T}^{s}_t} m_{it'})
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage2}\\
         & u_{it} \in [0, \max_j{\{H_j\}}]
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage_lower}\\
         & rut_{it} \leq rut_{i(t-1)} + H^{M} m_{it} - u_{it}
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\
        & rut_{i0} = Rut^{Init}_i
               & i \in \mathcal{I} \label{eq:rut_initial}\\
        & rut_{it} \geq H^{M} m_{it'}
                & t \in \mathcal{T}, t' \in \mathcal{T}^{s}_t, i \in \mathcal{I}\label{eq:rut_lower}\\ 
        & rut_{it} \in [0,H^{M}]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu}
    \end{align}
